\mytitle

### 2020-05-28 paper.tex
appendix yet again.
Minor edits on Appendix

Note that the ``N/A'' values in the table correspond to a particular situation arising from our use of two different energy functions, $E_{SS}$ and $E_{LS}$. For some problem instances an exact solver for \qcls{} finds and proves an optimal solution for the $E_{LS}$ objective. However, when that solution is evaluated using the $E_SS$ energy function, it has a lower energy than the solution found by the DA. This phenomenon is correct because the mapping from $E_{LS}$ to $E_{SS}$ does not necessarily preserve the ordering of solution quality. We do not include these instances in our speedup computations.

>>>>

Note that the ``N/A'' values in the table arise from our use of two different energy functions, $E_{SS}$ and $E_{LS}$. For some problem instances, an exact solver for \qcls{} finds and proves an optimal solution for the $E_{LS}$ objective but, when that solution is evaluated using the $E_{SS}$ energy function, it has a lower energy than the solution found by the DA. This phenomenon is correct because the mapping from $E_{LS}$ to $E_{SS}$ does not necessarily preserve the ordering of solution quality. We do not include these instances in our speedup computations.
